---
title: "Cross-checking maturity-, wt-, length-, and eggs-at-age with stock assessment figures"
author: "Mikaela Provost"
date: "August 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
# load functions
source("C:/Users/provo/Documents/GitHub/pfmc/src/life_table_calculations.r")

```
##1. Sardine: matches assessment

```{r}
# sardine 
# plot wt (kg) vs length (cm) --> matches stock assessment figure 3
plot(x=La_list$sardine,y=Ba_list$sardine,xlab="cm",ylab="kg",type="l")
# plot maturity*fecundity vs age --> matches stock assessment figure 5b
sardine_matxeggs <- eggs_list$sardine*prop_list$sardine
plot(sardine_matxeggs,ylab="eggs/kg (X1000)",type="l")
```

##2. Mackerel:
```{r}
# mackerel ---
# currently a problem species
```

##3. Yellowfin tuna:

##4. Bigeye tuna:

##5. Bluefin tuna:

##6. Bocaccio: matches assessment
```{r}
# bocaccio 
# plot eggs vs (this matches)
plot(x=Ba_list$bocaccio,y=eggs_list$bocaccio,
     ylab="eggs/kg (1000)",xlab="kg",type="l")
# plot kg vs cm (matches assessment, figure 13)
plot(x=La_list$bocaccio,y=Ba_list$bocaccio,
     ylab="kg",xlab="cm",type="l",
     xlim=c(0,85),ylim=c(0,8))
# plot cm vs age
plot(La_list$bocaccio,ylab="cm",xlab="age",type="l")
# plot prop mat*eggs vs cm (this does not)
plot(x=La_list$bocaccio,y=(eggs_list$bocaccio), 
     ylab="eggs/kg",xlab="cm",type="l",
     xlim=c(10,80),ylim=c(0,2000))
```

##7. Cabezon: matches assessment
```{r}
# cabezon 
# plot prop mature vs cm and age (matches assessment, fig 7)
plot(x=La_list$cabezon,y=prop_list$cabezon,
     xlab="cm",ylab="maturity",type="l")
plot(prop_list$cabezon,xlab="age",ylab="maturity",type="l")
# plot cm vs age (matches assessement, fig 8)
plot(La_list$cabezon,xlab="age",ylab="cm",type='l')
# plot eggs vs age (matches assessment)
plot(eggs_list$cabezon,ylab="eggs/kg (1000s)",xlab="age",type = "l")
plot(Ba_list$cabezon,ylab="kg",xlab="age",type = "l")
```

##8. Canary: matches assessment
```{r}
# canary 
# plot eggs vs kg (matches assessment, fig 35)
plot(y=eggs_list$canary, x=Ba_list$canary,
     ylab="eggs", xlab="kg",type="l")
# plot prop mat vs cm (matches assessment, fig 34)
plot(y=prop_list$canary, x=La_list$canary,
     ylab="maturity", xlab="cm",type="l")
# plot kg vs cm (matches assessment, fig 36 log scale)
plot(log10(Ba_list$canary), x=log10(La_list$canary),
     ylab="kg", xlab="cm",type="l")
```

##9. Chilipepper: matches assessment
```{r}

# chilipepper --- check ---
# plot kg vs cm
plot(y=Ba_list$chilipepper, x=La_list$chilipepper,
     ylab="kg", xlab="cm",type="l")
# plot maturity vs cm
plot(y=prop_list$chilipepper, x=La_list$chilipepper,
     ylab="maturity", xlab="cm",type="l")
# plot eggs vs kg
plot(y=eggs_list$chilipepper, x=Ba_list$chilipepper,
     ylab="eggs/kg", xlab="kg",type="l",
     ylim=c(0,200),xlim=c(0,1.2))
# plot eggs vs cm
plot(y=eggs_list$chilipepper, x=La_list$chilipepper,
     ylab="eggs/kg", xlab="cm",type="l",
     ylim=c(0,300),xlim=c(10,50))
# plot eggs*prop vs cm
plot(y=(eggs_list$chilipepper*prop_list$chilipepper),
     x=La_list$chilipepper,
     ylab="eggs*prop mature", xlab="cm",type="l",
     ylim=c(0,300),xlim=c(10,50))
```

##10. Darkblotched: matches assessment
```{r}
# darkblotched --- check ---
# plot cm at age (matches assessment, fig 42)
plot(La_list$darkblotched[1:20],ylab="cm",
     xlab="age",type="l")
# plot kg vs cm (matches assessment, fig 43)
plot(y=Ba_list$darkblotched,x=La_list$darkblotched,
     ylab="kg",xlab="cm",type="l")
# plot maturity vs cm (matches assessment, fig 44)
plot(y=prop_list$darkblotched,x=La_list$darkblotched,
     ylab="maturity",xlab="cm",type="l")
# plot eggs*prop vs cm (matches assessment, fig 46)
plot(y=(prop_list$darkblotched*eggs_list$darkblotched),
     x=La_list$darkblotched,
     ylab="eggs*prop",xlab="cm",type="l")
```

##11. Dover: matches assessment
```{r}
# dover 
# plot kg vs cm (matches assessment, fig25)
plot(y=Ba_list$dover,x=La_list$dover,
     ylab="kg",xlab="cm",type="l")
# plot maturity vs cm (matches assessment, fig26)
plot(y=prop_list$dover,x=La_list$dover,
     ylab="mature",xlab="cm",type="l")
# plot length at age (matches assessment, fig28)
plot(La_list$dover,
     ylab="cm",xlab="age",type="l")
```

##12. English: matches assessment
```{r}
# english --- check ---
# plot cm vs age (matches assessmetn, fig6)
plot(La_list$english,
     ylab="cm",xlab="age",type="l")
# plot maturity vs cm (matches assessment, fig8 mostly)
plot(y=prop_list$english,x=La_list$english,
     ylab="maturity",xlab="cm",type="l")
# plot eggs vs kg
plot(y=eggs_list$english,x=Ba_list$english,
     ylab="eggs",xlab="kg",type="l")
```

##13. Lingcod: matches assessment
```{r}
# lingcod --- check ---
# plot maturity vs length (matches assessment, fig94)
plot(y=prop_list$lingcod,x=La_list$lingcod,
     ylab="maturity",xlab="cm",type="l")
# plot egg*prop vs cm (matches assessment, fig95)
plot(y=(eggs_list$lingcod*prop_list$lingcod),x=La_list$lingcod,
     ylab="eggs*prop",xlab="cm",type="l")
# plot cm at age
plot(La_list$lingcod,
     ylab="cm",xlab="age",type="l",
     ylim=c(0,120),xlim=c(0,20))
```

##14. Hake: matches assessment (but a little unsure)
```{r}
# hake --- check (but unsure) ---
# plot maturity vs cm (matches assessment, fig11)
plot(y=prop_list$hake,x=La_list$hake,
     ylab="maturity",xlab="cm",type="l")
# plot eggs vs kg
plot(y=eggs_list$hake,x=Ba_list$hake,
     ylab="eggs",xlab="kg",type="l")
```

##15. POP: 

##16. Petrale: matches assessment
```{r}
# petrale 
# plot cm at age (matches assessment, fig13)
plot(La_list$petrale,
     ylab="cm",xlab="age",type="l")
# plot kg vs cm (matches assessment, fig23)
plot(y=Ba_list$petrale,x=La_list$petrale,
     ylab="kg",xlab="cm",type="l")
# plot maturity vs cm (matches assessment, fig24)
plot(y=prop_list$petrale,x=La_list$petrale,
     ylab="maturity",xlab="cm",type="l")
# plot eggs*prop vs cm (matches assessment, fig25)
plot(y=(eggs_list$petrale*prop_list$petrale),x=La_list$petrale,
     ylab="eggs*prop",xlab="cm",type="l")
```

##17. Sablefish: matches assessment
```{r}
# sablefish 
# plot maturity vs cm (matches assessment, fig30)
plot(y=prop_list$sablefish,x=La_list$sablefish,
     ylab="maturity",xlab="cm",type="l")
# plot cm at age (matches assessment, fig61)
plot(La_list$sablefish,
     ylab="cm",xlab="age",type="l")
```

##18. Window: matches assessment
```{r}
# window
# plot kg vs cm (matches assessment, fig41)
plot(y=Ba_list$window,x=La_list$window,
     ylab="kg",xlab="cm",type="l")
# plot maturity vs cm (matches assessment, fig42)
plot(y=prop_list$window,x=La_list$window,
     ylab="maturity",xlab="cm",type="l")
# plot cm at age (matches assessment, fig45)
plot(La_list$window,
     ylab="cm",xlab="age",type="l")
```

##19. Coho:

##20. Chinook:
