---
title: "parms"
author: "Mikaela Provost"
date: "March 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
# load packages
```

## Gathering parameters for PMFC species

I'm gathering parameters for XX species which are managed by the Pacific Fisheries Management Council (see <https://www.pcouncil.org/>). A lot of the life history information I need is stored on Fishbase. Instead of clicking on each species webpage and recording life history values I'm going to webscrape Fishbase website to record this information. 

```{r}
Common_name <- c("Pacific Sardine","Pacific Mackerel")
#library(knitr)
#kable(inserttablehere, caption = "table caption here.")
```


## Column names in parms.csv
1. **propmatFUN** -- age, length, check. Logistic function is in terms of age or length. 
+ 2 columns: propmat_inflection and propmat_slope
2. **growthFUN** -- 'schnute', 'vonb', 'check'. What kind of growth function (converts age to cm)
+ 8 columns: L1,L2,t1,t2,Ksch,Kvonb,tknot,tknot,Linf
3. **eggsFUN** -- fun1, fun2, vector, check. Function to calculate eggs from wieght. Fun1 is `eggs=W*(a+b*W)`. Fun2 is `b+a*W`. 
+ 2 columns: eggsslope, eggsintercept