---
title: "Ch 2 Plots"
author: "Mikaela Mikaelast"
date: "August 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, warning=FALSE, message=FALSE}
# RUN
# by: mikaela Mikaelast
# last edited: Aug 1, 2019
# ===================================================================


library(tidyr)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(directlabels)
library(grid)
library(lattice)
library(tidyverse)
library(tidycensus)
library(ggrepel)
library(biwavelet)
library(data.table)
#install.packages("ggpubr")
library(ggpubr)
# *************************************** #
# Plan:
# (1) run script to calculate life table information and load parms df
# (2) assemble Leslie matrices for different F values
# (3) simulate time series 
# (4) calculate spectra



# *************************************** #
# (1) run script to get life table information, parms df, and functions
source("C:/Users/Mikaela/Documents/GitHub/pfmc/src/life_table_calculations.r")


# *************************************** #
# (2) assemble Leslie matrices for different F values

# make all LEPs equal
conLEP = 5 #1.1
# adjust fecundities by this much
adjFec = round(1/conLEP,digits=1)

# Find F values that correspond to Exploitation Index values (BEFORE LEP=1.1)
# EI_F_before1.1_L <- as.list(rep(NA,length=length(parms$spp)))
# names(EI_F_before1.1_L) <- parms$spp
# system.time(for (i in 1:length(EI_F_before1.1_L)){ #for each spp
#   if(parms[parms$spp == parms$spp[i],]$problem_spp == "yes") {#if a problem, then
#     EI_F_before1.1_L[[i]] <- "problem"} #temporarily save in problemhold
#   else {
#     targetF <- calculate_F_from_EI(EI=c(0,0.4,0.6,0.8,0.95),
#                                maxage=as.numeric(parms[parms$spp == parms$spp[i],]$maxage),
#                                L_a=La_list[[i]],
#                                B_a=Ba_list[[i]],
#                                propmat_a=prop_list[[i]],
#                                eggs_a=eggs_list[[i]],
#                                vul_a=vul_list[[i]],
#                                M=as.numeric(parms[parms$spp == parms$spp[i],]$M),
#                                Fvals_many=seq(from=0,to=100,by=0.1))
#     targetF$spp <- rep(parms$spp[i],length=length(targetF[,1]))
#     EI_F_before1.1_L[[i]] <- targetF
#   }
# })
# EI_F_before1.1 <- bind_rows(EI_F_before1.1_L)

# ***
#parms <- parms[parms$problem_spp=="no",]
Fvals=seq(from=0,to=2,by=0.001)
A3d_list = as.list(rep(NA,length(parms$spp))) #Leslie arrays in list
LTABLE_list <- as.list(rep(NA,length(parms$spp))) #LTABLE arrays in list
names(A3d_list) <- parms$spp
names(LTABLE_list) <- parms$spp
eigan1 <- matrix(NA,nrow=length(Fvals),ncol=length(parms$spp))
eigan12 <- matrix(NA,nrow=length(Fvals),ncol=length(parms$spp))
LEPs <- matrix(NA,nrow=length(Fvals),ncol=length(parms$spp))
constLEP <- matrix(NA,nrow=length(Fvals),ncol=length(parms$spp))
EI_F_LEP1.1_L <- as.list(rep(NA,length=length(parms$spp)))
names(EI_F_LEP1.1_L) <- parms$spp


system.time(for (i in 1:length(parms$spp)){ #for each spp
  
  if(parms[parms$spp == parms$spp[i],]$problem_spp == "yes") {#if a problem, then
    problemshold <- parms$spp[i]} #temporarily save in problemhold
  else {
  # define parms for spp i
  M = as.numeric(parms[parms$spp == parms$spp[i],]$M)
  maxage = as.numeric(parms[parms$spp == parms$spp[i],]$maxage)
  
  # create empty arrays for Leslie and LTABLE, vectors for eigens 
  A3d <- array(NA,c(maxage,maxage,length(Fvals)))
  LTABLE3d <- array(NA,c(maxage,15,length(Fvals))) #12 cols
  e1 <- rep(NA,length=length(Fvals))
  e2 <- rep(NA,length=length(Fvals))
  e12 <- rep(NA,length=length(Fvals))
  lep <- rep(NA,length=length(Fvals))
  
  # assemble Leslie for each value of Fvals
  for(f in 1:length(Fvals)){
    out <- assemble_Leslie(maxage=maxage,
                           L_a=La_list[[i]],
                           B_a=Ba_list[[i]],
                           propmat_a=prop_list[[i]],
                           eggs_a=eggs_list[[i]],
                           vul_a=vul_list[[i]],
                           M=M,
                           Fval=Fvals[f]) #F=0, change this if want fishing
    LTABLE3d[,,f] <- data.matrix(out$LTABLE) #store LTABLE in 3d array
    
    # calculate LEP at F=0 (use this value of LEP to standardize unfished fecundity)
    lep_unfished = sum(out$LTABLE$LEP_a)
    
    # Asim = adjust fecundities so LEP equal for all species - simulation matrix
    Asim <- out$A
    Asim[1,] <- (Asim[1,]/(lep_unfished*adjFec))
    A3d[,,f] <- Asim
    
    # Aeig = adjust fecundities and multiply by k - eigen analysis matrix
    Aeig <- out$A
    Aeig[1,] <- (Aeig[1,]/(lep_unfished*adjFec)) # *Fvals[f]
    
    # re-calculate new LEP w/o F (should equal conLEP)
    term <- rep(NA,length=maxage)
    for(a in 1:maxage){term[a] <- Asim[1,a]*out$LTABLE$Survship[a]} #fecundity*survivorship
    constLEP[f,i] <- sum(term) #plotting 'term' is the spawning distribution over age
    rm(term,a)
    
    # calculate LEP w/F
    term <- rep(NA,length=maxage)
    for(a in 1:maxage){term[a] <- Asim[1,a]*out$LTABLE$Survship_Fing[a]} #fec*survshp w/F
    LEPs[f,i] <- sum(term)
    rm(term,a)
    
    # extract lambda1, lambda2/lambda1
    e1[f] = extract_first_eigen_value(Aeig)
    e2[f] = extract_second_eigen_value(Aeig)
    e12[f] = e2[f] / e1[f]
    
    
  } #closes F loop
  EI_F_LEP1.1_L[[i]] <- calculate_F_from_EI_Leslie(A=A3d[,,1],
                             vul_a=vul_list[[i]],
                             Fval=Fvals,
                             M=as.numeric(parms$M[i]),
                             EI=c(0,0.4,0.6,0.8))
  #dimnames(A3d)[[3]] <-as.character(Fvals) #label the 3rd dim by Fvals
  saveFs <- which(Fvals %in% EI_F_LEP1.1_L[[i]]$matching_F) #where are Fs of interest?
  A3dsave <- A3d[,,saveFs] #save only Leslie matrices that match Fs
  
  A3d_list[[i]] <- A3dsave 
  LTABLE_list[[i]] <- LTABLE3d
  eigan1[,i] <- e1
  eigan12[,i] <- e12
  LEPs[,i] <- lep
  #clean up before next i in loop
  #rm(A3d,LTABLE3d,out,M,maxage) 
  } #closes 'else' bracket for non-problem species.
  print(i)
}) #closes spp loop
rm(i,f,M,maxage,problemshold,lep,A3d,A3dsave,saveFs) #clean up


# *************************************** #
# () Calculate metrics from spawning distribution
# *************************************** #
# script below generates df 'spawndistmetrics' which has metric info
# keep only non-problem spp, convert numeric variables to numbers
# add metric info to ts.data
source("C:/Users/Mikaela/Documents/GitHub/pfmc/src/spawning_distributions.r")
spawndistmetrics <- spawndistmetrics[spawndistmetrics$problem_spp == "no",]
spawndistmetrics$mode_age <- as.numeric(as.character(spawndistmetrics$mode_age))
spawndistmetrics$sd_mode <- as.numeric(as.character(spawndistmetrics$sd_mode))
spawndistmetrics$cvs_mode <- as.numeric(as.character(spawndistmetrics$cvs_mode))
spawndistmetrics$maxage <- as.numeric(as.character(spawndistmetrics$maxage))
spawndistmetrics$spp <- as.character(spawndistmetrics$spp)
```

```{r echo=FALSE, fig.width=5, fig.height=8, warning=FALSE}
#tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/spawning_distribution_v2.tiff', units="in", width=12, height=9, res=300)
#do.call(grid.arrange,c(psub,ncol=2,left="Pr(spawning)"))
#dev.off()
```

Figure 1. Distribution of spawning biomass across ages. Dashed line and number indicate peak spawning age, standard deviation and coefficient of variation are listed at the top of each subplot. Distributions are probability of spawning at age: LEP-at-age/total LEP, where LEP-at-age is a function of egg production at age, probability of being mature, and survival from age 1 to age a.

```{r echo=FALSE,fig.width=8, fig.height=4, warning=FALSE}

peak_max <- ggplot(data=spawndistmetrics,aes(x=maxage,y=mode_age)) +
  geom_point() +
  geom_text_repel(data=spawndistmetrics,
                  aes(label = spp),
                  segment.color = "grey",
                  size = 2,
                  na.rm = TRUE)+
  theme_classic() + ylab("Peak spawning age") + xlab("Maximum age") 
  
sd_max <- ggplot(data=spawndistmetrics,aes(x=maxage,y=sd_mode)) +
  geom_point() +
  geom_text_repel(data=spawndistmetrics,
                  aes(label = spp),
                  segment.color = "grey",
                  size = 2,
                  na.rm = TRUE)+
  theme_classic() + ylab("Spawning distribution Stdev") + xlab("Maximum age") 
grid.newpage()
grid.draw(cbind(ggplotGrob(peak_max), ggplotGrob(sd_max), size = "last"))
rm(peak_max,sd_max)
```

Figure 2. The relationship between (a) peak spawning age and maximum age, and (b) standard deviation of the spawning biomass distribution and maximum age. 


```{r echo=FALSE,fig.width=8, fig.height=4,warning=FALSE}
std_peak <- ggplot(data=spawndistmetrics,aes(x=mode_age,y=sd_mode)) +
  geom_point() +
  geom_text_repel(data=spawndistmetrics,
                  aes(label = spp),
                  segment.color = "grey",
                  size = 2,
                  na.rm = TRUE)+
  theme_classic() + ylab("Spawning distribution Stdev") + xlab("Peak spawning age")

cv_peak <- ggplot(data=spawndistmetrics,aes(x=mode_age,y=cvs_mode)) +
  geom_point() +
  geom_text_repel(data=spawndistmetrics,
                  aes(label = spp),
                  segment.color = "grey",
                  size = 2,
                  na.rm = TRUE)+
  theme_classic() + ylab("Spawning distribution CV") + xlab("Peak spawning age")
grid.newpage()
grid.draw(cbind(ggplotGrob(std_peak), ggplotGrob(cv_peak), size = "last"))
rm(std_peak,cv_peak)
```

Figure 3. (a) Standard deviation of spawning distribution vs peak spawning age. (b) Spawning distribution CV vs peak spawning age. 

```{r include=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# *************************************** #
# (3) Simulate pops. Loop over Aarray list to simulate using different Leslie matrices 
# *************************************** #
# Generate 3d Leslie arrays for EIlevels
summary(Fvals)
FLEPlevels = c(1,0.8,0.6,0.35,0.3)
EIlevels=round((1-FLEPlevels)/0.9,digits=2)
#EIlevels=c(0,0.3,0.5,0.76,0.77,0.78) #last number corresponds to FLEP=0.3
#FLEPlevels=1-(0.9*EIlevels)
#FLEPlevels=round(1-(EIlevels*0.9),digits=2)

A3d_list <- generate3dLeslie(spp=parms[parms$problem_spp=="no",]$spp,
                             Fvals=Fvals,
                             EIlevels=EIlevels)



# Generate noise time series 
set.seed(62) #Set the seed so that every white ts uses same random sequence
timesteps=5000
rm_first_timesteps = 2000
# Noise signals
white <- rnorm((timesteps-2),mean=0,sd=1) # white noise
enso_ts_reps <- read.csv(file="C:/Users/Mikaela/Documents/GitHub/pfmc/parms_data/simulated_MEI.csv",header=TRUE) 
ensoS_ts_reps <- read.csv(file="C:/Users/Mikaela/Documents/GitHub/pfmc/parms_data/simulated_MEI_lowfreq.csv",header=TRUE) 
ensoF_ts_reps <- read.csv(file="C:/Users/Mikaela/Documents/GitHub/pfmc/parms_data/simulated_MEI_highfreq.csv",header=TRUE) 

# make sure same length as white
enso1 <- enso_ts_reps[,10][1:length(white)]
ensoF <- ensoF_ts_reps[,10][1:length(white)]
ensoS <- ensoS_ts_reps[,10][1:length(white)]
noisenames <- c("white","ENSO","ENSOfast","ENSOslow")
noisetypes <- list(white,enso1,ensoF,ensoS)
names(noisetypes) <- noisenames
# check total variance in signals
enso1 <- (enso1-mean(enso1))/sd(enso1)
ensoF <- (ensoF-mean(ensoF))/sd(ensoF)
ensoS <- (ensoS-mean(ensoS))/sd(ensoS)
# mean(enso1)/sd(enso1)
# mean(ensoF)/sd(ensoF)
# mean(ensoS)/sd(ensoS)
# sd(enso1)
# sd(ensoF)
# sd(ensoS)
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/noise_white.tiff', units="in", width=5, height=4, res=300) 
# plot(white[1:100],type="l",ylim=c(-3,3),main="white",xlab="Year",ylab="")
# dev.off()
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/noise_enso.tiff', units="in", width=5, height=4, res=300) 
# plot(enso1[1:100],type="l",ylim=c(-3,3),main="ENSO (historical)",xlab="Year",ylab="")
# dev.off()
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/noise_ensoF.tiff', units="in", width=5, height=4, res=300) 
# plot(ensoF[1:100],type="l",ylim=c(-3,3),main="ENSO 2x",xlab="Year",ylab="")
# dev.off()
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/noise_ensoS.tiff', units="in", width=5, height=4, res=300) 
# plot(ensoS[1:100],type="l",ylim=c(-3,3),main="ENSO 0.5x",xlab="Year",ylab="")
# dev.off()

# load simulation model:
source("C:/Users/Mikaela/Documents/GitHub/pfmc/src/simulation_model.r")

# Generate table of ts for plotting 
# note: alpha > 1/LEP. Since I set LEP=5 for all spp, alpha must be > 1/5
ts.L <- as.list(rep(NA,length=length(noisenames)))

for(n in 1:length(noisenames)){
  ts <- simulate_spp(noise = noisetypes[[n]],
                        timesteps = timesteps,
                        rm_first_timesteps = rm_first_timesteps, #burn in time
                        alphas = 1, #for BH
                        betas = 5000, #for BH
                        span.multiplier = 1, #not sure I need this yet
                        EIlevels = EIlevels, #vector of EI levels, 1st is OFL--match
                        OFL = max(EIlevels), #FLEP associated with OFL
                        List_of_Leslie3d = A3d_list, #should have F vals associated with FLEPlevels
                        spp = parms[parms$problem_spp == "no",]$spp,
                        sig_r=0.5)
  ts$noise <- rep(noisenames[n],length=length(ts[,1]))
  ts.L[[n]] <- ts   }
# convert list into one data frame
ts.data <- bind_rows(ts.L,id=NULL)
# add column with corresponding FLEP
ts.data$FLEP <- round(1-(ts.data$EI*0.9),digits=2)
rm(ts.L,n,ts)

# -------------------------------------------------------
# Plot ts w/white and ENSO noise and threshold
# ts is with harvest rate such that FLEP=0.4 or 0.45 
# threshold = mean level of eggs/recruits/N when FLEP=0.3
# #ts.data$EI <- as.character(ts.data$EI)
# spp = parms[parms$problem_spp == "no",]$spp
# multiplots <- as.list(rep(NA,length(spp)))
# names(multiplots) <- spp
#spp = parms[parms$spp == "Darkblotched",]$spp
#minSSB = 15000
#maxSSB = 50000
# for(n in 1:length(noisenames)){
#   multiplots <- as.list(rep(NA,length(spp)))
#   names(multiplots) <- spp
#   dfts <- ts.data[ts.data$FLEP==0.35 &
#                 ts.data$variable=="Nsize" &
#                 ts.data$noise==noisenames[n] &
#                 ts.data$year %in% rm_first_timesteps:(timesteps-2600),]
#   dfth <- ts.data[ts.data$FLEP==0.3 &
#                 ts.data$variable=="Nsize" &
#                 ts.data$noise==noisenames[n] &
#                 ts.data$year %in% rm_first_timesteps:(timesteps-2600),]
#   minSSB <- if(dfth$means[1] < min(dfts$value)){dfth$means[1]}else{min(dfts$value)}
#   maxSSB <- max(dfts$value)


  
# -------------------------------------------------------
# Calculate probability of exceeding overfishing limit
# for each variable type in both types of noise
probs <- array(NA,c(length(unique(ts.data$noise)),
                    length(unique(ts.data$variable)),
                    length(unique(ts.data$spp)))) 

for(s in 1:length(unique(ts.data$spp))) {
  for(n in 1:length(unique(ts.data$noise))) {
    for(v in 1:length(unique(ts.data$variable))) {
      #subset the right time series
      vals <- ts.data[ts.data$spp==unique(ts.data$spp)[s] &
        ts.data$variable==unique(ts.data$variable)[v] &
        ts.data$noise==unique(ts.data$noise)[n] &
        ts.data$FLEP==0.35 &
        ts.data$year %in% rm_first_timesteps:(timesteps-2600),]$value
      #pull out the right threshold value
      threshold <- ts.data[ts.data$spp==unique(ts.data$spp)[s] &
        ts.data$variable==unique(ts.data$variable)[v] &
        ts.data$noise==unique(ts.data$noise)[n] &
        ts.data$FLEP==0.3,]$means[1] #only need 1 value

      # calc probability: # of timesteps below threshold/total timesteps
      probs[n,v,s] <- sum(vals < threshold) / length(vals)
    }
  }
}
rm(s,n,v,threshold,vals)
variable_type <- unique(ts.data$variable)
ndf <- as.list(rep(NA,length(unique(ts.data$noise))))
for(n in 1:length(unique(ts.data$noise))){
  df <- as.data.frame(probs[n,,]) #select rec,egg,N ts for all spp in n noise
  df <- bind_cols(as.data.frame(variable_type),
                  as.data.frame(rep(unique(ts.data$noise)[n],length(df[,1]))),
                  df)
  colnames(df) <-  c("variable","noise",spp)
  df <- df %>% gather(key="spp",value="probs",3:ncol(df))
  ndf[[n]] <- df}
probdf <- bind_rows(ndf,id=NULL)
rm(n,df,ndf,probs)
# fill in probdf with age structure characteristics
probdf$peak <- spawndistmetrics[match(probdf$spp,spawndistmetrics$spp),"mode_age"]
probdf$cvs <- spawndistmetrics[match(probdf$spp,spawndistmetrics$spp),"cvs_mode"]
probdf$maxage <- spawndistmetrics[match(probdf$spp,spawndistmetrics$spp),"maxage"]
probdf$stdev <- spawndistmetrics[match(probdf$spp,spawndistmetrics$spp),"sd_mode"]



# # Plot p(OFL) vs max age, peak, CV, and stdev of spawning biomass distribution
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/agestructure_vs_probs_Nsize.tiff', units="in", width=8, height=11, res=300) 
# p1 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=maxage,y=probs,color=spp)) +
#   geom_point() + facet_grid(vars(noise)) + ggtitle("(1a) Fraction of SSB time series\n that is below mean recruitment\n when FLEP=0.3 (the assumed OFL) vs max age") +
#   theme(plot.title = element_text(size=8))
# p2 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=maxage,y=probs,color=noise)) +
#   geom_point()  + ggtitle("(1b) Similar plot as 1a, but color-coded by noise")+
#   theme(plot.title = element_text(size=8))
# 
# p3 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=cvs,y=probs,color=spp)) +
#   geom_point() + facet_grid(vars(noise)) + ggtitle("(2a) Fraction of SSB time series\n that is below mean recruitment\n when FLEP=0.3 (the assumed OFL) vs CV")+
#   theme(plot.title = element_text(size=8))
# p4 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=cvs,y=probs,color=noise)) +
#   geom_point()  + ggtitle("(2b) Similar plot as 2a, but color-coded by noise")+
#   theme(plot.title = element_text(size=8))
# 
# p5 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=peak,y=probs,color=spp)) +
#   geom_point() + facet_grid(vars(noise)) + ggtitle("(3a) Fraction of SSB time series\n that is below mean recruitment\n when FLEP=0.3 (the assumed OFL) vs peak age")+
#   theme(plot.title = element_text(size=8))
# p6 <- ggplot(data=probdf[probdf$variable=="Nsize" ,],aes(x=peak,y=probs,color=noise)) +
#   geom_point()  + ggtitle("(3b) Similar plot as 3a, but color-coded by noise")+
#   theme(plot.title = element_text(size=8))
# 
# pplots <- list(p1,p2,p3,p4,p5,p6)
# do.call(grid.arrange,c(pplots,ncol=2))
# dev.off()

# # -------------------------------------------------------
# # Test: do the raw timeseries of biomass and timeseries
# # when CV has been standardized to 1 look the same?
# # ANSWER: Yes. Note=can't plot log() scale
# tempts <- ts.data[ts.data$spp==spp[1] &
#                     ts.data$FLEP==1 &
#                     ts.data$variable=="recruits" &
#                     ts.data$noise %in% c("white") &
#                     ts.data$year %in% rm_first_timesteps:(timesteps-2),]
# values.mean0 <- (tempts$value-mean(tempts$value))/sd(tempts$value)
# tempts.mean0 <- as.data.frame(cbind(tempts$year,values.mean0))
# colnames(tempts.mean0) <- c("year","value")
# head(tempts.mean0)
# temp1 <- tempts.mean0
# temp1 <- tempts.mean0
# # ggplot(data=tempts.mean0,aes(x=year,y=value)) +
# #       geom_line() +
# #       
# #       ylab("Spawning stock biomass") +
# #       theme_bw() 
# sptest <- spec.pgram(temp1$value,spans=c(m,m),
#                         taper=0.1,plot=FALSE,demean=TRUE)
# d1 <- as.data.frame(cbind(sptest$freq,sptest$spec))
# colnames(d1) <- c("freq","sp")
# sptest <- spec.pgram(temp12$value,spans=c(m,m),
#                         taper=0.1,plot=FALSE,demean=TRUE)
# d2 <- as.data.frame(cbind(sptest$freq,sptest$spec))
# colnames(d2) <- c("freq","sp")
# 
# ggplot(data=d1,aes(x=freq, y=sp)) +
#   geom_line() + scale_y_log10()
#   geom_line(data=d1,aes(x=freq,y=sp))+
#   scale_y_log10()
# -------------------------------------------------------
# Calculate spectra in time series
# 1) create df w/spec for different noises
ts.for.spec <- ts.data
ts.for.spec$spec <- rep(NA,length(ts.for.spec[,1]))
ts.for.spec <- ts.for.spec[ts.for.spec$year %in% rm_first_timesteps:(timesteps-2),]
span.multiplier= 1
# setting 'span' - a vector of odd integers to specify the smoothers
# sq root of timeseries lgth, rounded
# make it odd, if the square root is even
tmp <- ceiling(sqrt(length(1:(timesteps-rm_first_timesteps-2)))) 
if (tmp %% 2 == 0) {m <- tmp+1} else {m <- tmp} 
m = m * span.multiplier

df.sppL <- as.list(rep(NA,length(unique(ts.for.spec$spp))))
names(df.sppL) <- unique(ts.for.spec$spp)
# for each species...
for (s in 1:length(unique(ts.for.spec$spp))){
  df.EIL <- as.list(rep(NA,length(unique(ts.for.spec$EI))))
  names(df.EIL) <- unique(ts.for.spec$EI)
  # and for each exploitation level...
  for(e in 1:length(unique(ts.for.spec$EI))){
    df.varL <- as.list(rep(NA,length(unique(ts.for.spec$variable))))
    names(df.varL) <- unique(ts.for.spec$variable)
    # and for each type of output data (eggs, recruits, N)...
    for(v in 1:length(unique(ts.for.spec$variable))){
      df.noiseL <- as.list(rep(NA,length(unique(ts.for.spec$noise))))
      names(df.noiseL) <- unique(ts.for.spec$noise)
      # and for each type of noise...
      # calculate the spectrum in the time series
      for(n in 1:length(unique(ts.for.spec$noise))){
        ts <- ts.for.spec[ts.for.spec$spp==unique(ts.for.spec$spp)[s] &
                      ts.for.spec$EI==unique(ts.for.spec$EI)[e] &
                      ts.for.spec$variable==unique(ts.for.spec$variable)[v] &
                      ts.for.spec$noise==unique(ts.for.spec$noise)[n],]$value
        
        # ---
        # Chunk 1: Run if I want to standardize CV in ts
        ts.mod <- (ts-mean(ts))/sd(ts) 
        # ---
        # Chunk 2: Run if I DON'T want to standardize CV
        #ts.mod <- ts
        # ---
        sp = spec.pgram(ts.mod,spans=c(m,m),
                        taper=0.1,plot=FALSE,demean=TRUE)
        #divide each value of spec by the area under the curve
        specN <- as.numeric(sp$spec/sum(sp$spec)) # sum(specN)=1
        spec <- sp$spec # sum(spec) not equal 1
        freq <- sp$freq
        noise <- rep(unique(ts.for.spec$noise)[n],length(freq))
        df=data.frame(cbind(spec,specN,freq,noise))
        df.noiseL[[n]]=df
        print(unique(ts.for.spec$noise)[n])
      }#close noise loop
      dfv <- bind_rows(df.noiseL,.id=NULL)
      dfv$variable <- rep(unique(ts.for.spec$variable)[v],length(dfv[,1]))
      df.varL[[v]]<-dfv
      print(unique(ts.for.spec$variable)[v])
    }#close variable loop
    dfe <- bind_rows(df.varL,.id=NULL)
    dfe$EI <- rep(unique(ts.for.spec$EI)[e],length(dfe[,1]))
    df.EIL[[e]]<-dfe
    print(unique(ts.for.spec$EI)[e])
  }#close EI loop
  dfs <- bind_rows(df.EIL,.id=NULL)
  dfs$spp <- rep(unique(ts.for.spec$spp)[s],length(dfs[,1]))
  df.sppL[[s]]<-dfs
  print(unique(ts.for.spec$spp)[s])
}
ts.spec <- bind_rows(df.sppL,.id=NULL) 
ts.spec$spec <- as.numeric(ts.spec$spec)
ts.spec$specN <- as.numeric(ts.spec$specN)
ts.spec$freq <- as.numeric(levels(ts.spec$freq))[ts.spec$freq]
# add spp age structure characteristics to table
ts.spec$peak <- spawndistmetrics[match(ts.spec$spp,spawndistmetrics$spp),"mode_age"]
ts.spec$maxage <- spawndistmetrics[match(ts.spec$spp,spawndistmetrics$spp),"maxage"]
ts.spec$cvs <- spawndistmetrics[match(ts.spec$spp,spawndistmetrics$spp),"cvs_mode"]
ts.spec$stdev <- spawndistmetrics[match(ts.spec$spp,spawndistmetrics$spp),"sd_mode"]
str(ts.spec)
rm(dfe,dfs,df.sppL,df.EIL,dfv,df.varL)

# # 2) calculate spec of ENSO
# ensosp <- spec.pgram(x=enso1[rm_first_timesteps:(timesteps-2)],
#                        spans=c(m,m),taper=0.1,plot = FALSE,demean = TRUE)
# # check length of spec for enso, should be same length as spec for spp
# if(length(ensosp$spec)==length(ts.spec[ts.spec$spp=="Sardine" &
#                                    ts.spec$EI==unique(ts.spec$EI)[1] &
#                                    ts.spec$noise==unique(ts.spec$noise)[1] &
#                                    ts.spec$variable==unique(ts.spec$variable)[1],1]) ){print("yes")}else{print("no")}
# # plot ENSO frequency content
# plot(x=ensosp$freq,y=ensosp$spec,xaxs = "i", yaxs = "i",
#      type = "l",log="y",yaxt="n",ylab="")
# 
# # 3) ENSO spectrum x pop spectrum in white noise = pop spectrum in ENSO
# multiplied.spec <- ts.spec[!ts.spec$noise=="ENSO",]
# multiplied.spec$noise <- rep("Spec w/white x ENSO",length(multiplied.spec[,1]))
# multiplied.spec$spec <- rep(NA,length(multiplied.spec[,1]))
# head(multiplied.spec)
# 
# for(s in 1:length(unique(ts.spec$spp))){
#   for(e in 1:length(unique(ts.spec$EI))){
#     for(v in 1:length(unique(ts.spec$variable))){
#       wh.spec <- ts.spec[ts.spec$spp==unique(ts.spec$spp)[s] &
#                          ts.spec$EI==unique(ts.spec$EI)[e] &
#                          ts.spec$variable==unique(ts.spec$variable)[v] &
#                          ts.spec$noise=="white",]$spec
#       multiplied.spec[multiplied.spec$spp==unique(multiplied.spec$spp)[s] &
#                       multiplied.spec$EI==unique(multiplied.spec$EI)[e] &
#                       multiplied.spec$variable==unique(multiplied.spec$variable)[v],]$spec <- wh.spec * ensosp$spec
#     }  } } 
# rm(s,e,v)
# multiplied.spec <- as.data.frame(multiplied.spec)
# ts.spec.combo <- rbind(ts.spec,multiplied.spec)
# 
# # 4) Plot overlapping spectrum
# overlap.specL <- as.list(rep(NA,length(unique(multiplied.spec$spp))))
# for(s in 1:length(unique(ts.spec.combo$spp))){
#   overlap.specL[[s]] <- ggplot(data=ts.spec.combo[ts.spec.combo$spp==unique(ts.spec.combo$spp)[s] &
#     ts.spec.combo$EI==0 &
#     ts.spec.combo$variable=="recruits" &
#     ts.spec.combo$noise %in% c("ENSO","Spec w/white x ENSO"),],
#     aes(x=freq,y=spec,color=noise)) +
#     geom_line() + scale_color_grey() +  
#     scale_y_log10(limits=c(min(ts.spec.combo$spec),max(ts.spec.combo$spec)),
#                   breaks=c(1e1,1e7)) +
#     ggtitle(unique(ts.spec.combo$spp)[s]) + 
#     theme_classic() + ylab("") + xlab("") +
#     theme(legend.title = element_blank(),legend.position=c(0.7,0.9))   }#end ggplot loop
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/Overlapping_spectra.tiff', units="in", width=7, height=13, res=300) 
# do.call(grid.arrange,c(overlap.specL,ncol=2,left="Sensitivity", bottom="Frequency"))
# dev.off()
# 
# # 5) Plot overlapping SSB spectra in white & ENSO 
# overlap.specL <- as.list(rep(NA,length(unique(ts.spec$spp))))
# names(overlap.specL) <- unique(ts.spec$spp)
# maxspec <- max(ts.spec[ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("white","ENSO"),]$specN)
# minspec <- min(ts.spec[ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("white","ENSO"),]$specN)
# for(s in 1:length(unique(ts.spec$spp))){
#   ts <- ts.spec[ts.spec$spp==unique(ts.spec$spp)[s] &
#     ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("white","ENSO"),]
#   overlap.specL[[s]] <- ggplot(data=ts,aes(x=freq,y=specN,linetype=noise)) +
#     geom_line() + scale_color_grey() +
#     scale_y_continuous(limits=c(minspec,maxspec),trans="log10") +
#     ggtitle(unique(ts.spec$spp)[s]) +
#     theme_classic() + ylab("") + xlab("") +
#     theme(legend.title = element_blank(),legend.position=c(0.7,0.9))
# }#end ggplot loop
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/Overlapping_spectra_whiteENSO_all10.tiff', units="in", width=6, height=12, res=300) 
# do.call(grid.arrange,c(overlap.specL,ncol=2,left="Sensitivity", bottom="Frequency"))
# dev.off()
# rm(overlap.specL,s,ts,maxspec,minspec)

# # 5) Plot overlapping SSB spectra in ENSO, ENSOfast, ENSOslow 
# overlap.specL <- as.list(rep(NA,length(unique(ts.spec$spp))))
# names(overlap.specL) <- unique(ts.spec$spp)
# maxspec <- max(ts.spec[ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("ENSO","ENSOfast","ENSOslow"),]$specN)
# minspec <- min(ts.spec[ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("ENSO","ENSOfast","ENSOslow"),]$specN)
# for(s in 1:length(unique(ts.spec$spp))){
#   ts <- ts.spec[ts.spec$spp==unique(ts.spec$spp)[s] &
#     ts.spec$EI==0 &
#     ts.spec$variable=="Nsize" &
#     ts.spec$noise %in% c("ENSO","ENSOfast","ENSOslow"),]
#   overlap.specL[[s]] <- ggplot(data=ts,aes(x=freq,y=specN,linetype=noise)) +
#     geom_line() + scale_color_grey() +
#     scale_y_continuous(limits=c(minspec,0.021),trans="log10") +
#     ggtitle(unique(ts.spec$spp)[s]) +
#     theme_classic() + ylab("") + xlab("") +
#     theme(legend.title = element_blank(),legend.position=c(0.7,1))
# }#end ggplot loop
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/Overlapping_spectra_ENSOfs_all10.tiff', units="in", width=8, height=10, res=300) 
# do.call(grid.arrange,c(overlap.specL,ncol=3,left="log10", bottom="Frequency",top="Overlapping SSB spectrum with ENSO, ENSO-fast, and ENSO-slow \n(SSB CV is constant across spp)"))
# dev.off()
# rm(overlap.specL,s,ts,maxspec,minspec)

# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/Overlapping_spectra_whiteENSO_all10_baseR.tiff', units="in", width=6, height=12, res=300) 
# par(mfrow=c(6,2),mai=c(0.2,0.3,0.2,0.2))
# for(i in 1:length(spp)){
#   plot(x=ts.spec[ts.spec$spp==spp[i] &
#                      ts.spec$noise=="ENSO" &
#                      ts.spec$variable=="Nsize" &
#                      ts.spec$EI==0,]$freq,
#          y=log10(ts.spec[ts.spec$spp==spp[i] &
#                      ts.spec$noise=="ENSO" &
#                      ts.spec$variable=="Nsize" &
#                      ts.spec$EI==0,]$specN),
#          type = "l",lty="solid",ylab="",xlab="frequency")
#   lines(x=ts.spec[ts.spec$spp==spp[i] &
#                      ts.spec$noise=="white" &
#                      ts.spec$variable=="Nsize" &
#                      ts.spec$EI==0,]$freq,
#          y=log10(ts.spec[ts.spec$spp==spp[i] &
#                      ts.spec$noise=="white" &
#                      ts.spec$variable=="Nsize" &
#                      ts.spec$EI==0,]$specN),
#          type = "l",lty="dashed",ylab="",xlab="frequency")
# 
# }
# dev.off()

# # -------------------------------------------------------
# # Plot wavelet multipanel plots - exports 2 images for each noise
# for(n in 1:length(noisenames)){
#   
#   plot_wvlt_CVnotstd_AUC1(burn_in_pd = rm_first_timesteps, #remove from beginning of ts
#                    num_rows2plt = 1000, #number of years to plot
#                    timesteps = timesteps,
#                    span.multiplier = 1,
#                    noise = noisetypes[[n]],
#                    noisename = noisenames[n],
#                    ts.data = ts.data, #timeseries dataset
#                    ts.spec = ts.spec, #spectrum dataset
#                    spawning_dist_data=spawning_dist_data)
#   print(noisenames[n])
#   
# }

# -------------------------------------------------------
# Calculate total variance in time series (stdev/mean)
# Use this to calculate absolute variance at high and low frequencies
fillList <- as.list(rep(NA,length(unique(ts.data$spp)))) 
names(fillList) <- unique(ts.data$spp)
for(s in 1:length(unique(ts.data$spp))){
  fillsdm <- array(NA,c(length(unique(ts.data$variable)),
                    length(unique(ts.data$noise)),
                    length(unique(ts.data$EI))))
  for(e in 1:length(unique(ts.data$EI))){
    for(n in 1:length(unique(ts.data$noise))){
      for(v in 1:length(unique(ts.data$variable))){
        stdev <- sd(ts.data[ts.data$spp==unique(ts.data$spp)[s] &
                            ts.data$EI==unique(ts.data$EI)[e] &
                            ts.data$noise==unique(ts.data$noise)[n] &
                            ts.data$variable==unique(ts.data$variable)[v],]$value[rm_first_timesteps:(timesteps-2)])
        m <- ts.data[ts.data$spp==unique(ts.data$spp)[s] &
                            ts.data$EI==unique(ts.data$EI)[e] &
                            ts.data$noise==unique(ts.data$noise)[n] &
                            ts.data$variable==unique(ts.data$variable)[v],]$mean[1]
        fillsdm[v,n,e] <- stdev/m
      }
    }
  }
  fillList[[s]] <- fillsdm
  print(unique(ts.data$spp)[s])
}

list.of.each.spp <- as.list(rep(NA,length(unique(ts.data$spp))))
names(list.of.each.spp) <- unique(ts.data$spp)
for(s in 1:length(fillList)){
  df <- fillList[[s]]
  list.of.each.EI <- as.list(rep(NA,length(unique(ts.data$EI))))
  names(list.of.each.EI) <- unique(ts.data$EI)
  
  for(e in 1:length(unique(ts.data$EI))){
    dfe <- as.data.frame(df[,,e])
    list.of.each.noise <- as.list(rep(NA,length(unique(ts.data$noise))))
    names(list.of.each.noise) <- unique(ts.data$noise)
    
    for(n in 1:length(unique(ts.data$noise))){
      dfn <- dfe[,n]
      d <- as.data.frame(cbind(unique(ts.data$variable),dfn,
                               rep(unique(ts.data$noise)[n])))
      colnames(d) <- c("variable","variance","noise")
      list.of.each.noise[[n]] <- d
      print(unique(ts.data$noise)[n])
    }
    dfnoise <- bind_rows(list.of.each.noise,.id=NULL)
    EI <- rep(unique(ts.data$EI)[e],length(dfnoise[,1]))
    dfnoise <- cbind(EI,dfnoise)
    list.of.each.EI[[e]] <- dfnoise
    print(unique(ts.data$EI)[e])
  }
  dfei <- bind_rows(list.of.each.EI,.id=NULL)
  spp <- rep(names(fillList)[s],length(dfei[,1]))
  dfei <- cbind(spp,dfei)
  list.of.each.spp[[s]] <- dfei
  print(unique(ts.data$spp)[s])
}
totalvar <- bind_rows(list.of.each.spp,.id=NULL)
# fill in totalvar with age structure characteristics
totalvar$peak <- spawndistmetrics[match(totalvar$spp,spawndistmetrics$spp),"mode_age"]
totalvar$cvs <- spawndistmetrics[match(totalvar$spp,spawndistmetrics$spp),"cvs_mode"]
totalvar$maxage <- spawndistmetrics[match(totalvar$spp,spawndistmetrics$spp),"maxage"]
totalvar$stdev <- spawndistmetrics[match(totalvar$spp,spawndistmetrics$spp),"sd_mode"]
totalvar$variance <- as.numeric(totalvar$variance)
rm(list.of.each.spp,dfei,spp,dfnoise,list.of.each.EI,list.of.each.noise,dfn)

# -------------------------------------------------------
# Calculate fraction & amount of variance at high & low freq

# 2 definitions for high and low frequencies: choose one!
# 1) threshold for high/low frequencies is 1/(2T) 
spawndistmetrics$AUCthresholdT <- 1/(spawndistmetrics$mode_age*2)
AUCthreshold_ordered_by_peak <- spawndistmetrics %>% arrange(mode_age) %>% pull(AUCthresholdT)
spp_ordered_by_peak <- spawndistmetrics %>% arrange(mode_age) %>% pull(spp)

# 2) threshold could be the same for all pops:
AUCthreshold10 <- rep(0.1,length=length(spawndistmetrics[,1]))
spawndistmetrics <- cbind(spawndistmetrics,AUCthreshold10)

# Fraction of H/L - AUC equals 1
# Amount of H/L - AUC equals amount, sum 'spec' for freq 
# Amount of H/L - multiply totalvar by fraction of AUC
AUC_amount_highL <- as.list(rep(NA,length=length(noisenames)))
AUC_amount_lowL <- as.list(rep(NA,length=length(noisenames)))
AUC_fraction_highL <- as.list(rep(NA,length=length(noisenames)))
AUC_fraction_lowL <- as.list(rep(NA,length=length(noisenames)))
TOT_highL <- as.list(rep(NA,length=length(noisenames)))
TOT_lowL <- as.list(rep(NA,length=length(noisenames)))
AUC_totalamt_L <- as.list(rep(NA,length=length(noisenames)))

names(AUC_amount_highL) <- noisenames
names(AUC_amount_lowL) <- noisenames
names(AUC_fraction_highL) <- noisenames
names(AUC_fraction_lowL) <- noisenames
names(AUC_totalamt_L) <- noisenames
names(TOT_highL) <- noisenames
names(TOT_lowL) <- noisenames

# frequency increament
freq <- min(ts.spec$freq)

for (n in 1:length(noisenames)){ #for each noise type...
  
  #empty dfs for high var at high freq
  AUC_amount_high <- rep(NA,length=length(spp_ordered_by_peak))
  AUC_fraction_high <- rep(NA,length=length(spp_ordered_by_peak))
  TOT_high <- rep(NA,length=length(spp_ordered_by_peak))
  #empty dfs for low var at high freq
  AUC_amount_low <- rep(NA,length=length(spp_ordered_by_peak))
  AUC_fraction_low <- rep(NA,length=length(spp_ordered_by_peak))
  TOT_low <- rep(NA,length=length(spp_ordered_by_peak))
  
  AUC_totalamt <- rep(NA,length=length(spp_ordered_by_peak))
  
  for (s in 1:length(spp_ordered_by_peak)){ #for each spp...
    
    # ** Check inequality sign for percent high or low variability **
    # multiply ht of each bar under curve by the width (one unit of x, freq)
    AUC_amount_high[s] <- sum(ts.spec[ts.spec$variable == "Nsize" 
                                  & ts.spec$EI==0.72
                                  & ts.spec$spp==spp_ordered_by_peak[s]
                                  & ts.spec$noise==noisenames[n]
                                  & ts.spec$freq > AUCthreshold_ordered_by_peak[s],]$spec)
                               # > is for amount of high, =< is for amount of low
    AUC_amount_low[s] <- sum(ts.spec[ts.spec$variable == "Nsize" 
                                  & ts.spec$EI==0.72
                                  & ts.spec$spp==spp_ordered_by_peak[s]
                                  & ts.spec$noise==noisenames[n]
                                  & ts.spec$freq <= AUCthreshold_ordered_by_peak[s],]$spec)
    AUC_fraction_high[s] <- sum(ts.spec[ts.spec$variable == "Nsize" 
                                  & ts.spec$EI==0.72
                                  & ts.spec$spp==spp_ordered_by_peak[s]
                                  & ts.spec$noise==noisenames[n]
                                  & ts.spec$freq > AUCthreshold_ordered_by_peak[s],]$specN)
    
    AUC_fraction_low[s] <- sum(ts.spec[ts.spec$variable == "Nsize" 
                                  & ts.spec$EI==0.72
                                  & ts.spec$spp==spp_ordered_by_peak[s]
                                  & ts.spec$noise==noisenames[n]
                                  & ts.spec$freq <= AUCthreshold_ordered_by_peak[s],]$specN)
    
    AUC_totalamt[s] <- sum(ts.spec[ts.spec$variable == "Nsize" 
                                  & ts.spec$EI==0.72
                                  & ts.spec$spp==spp_ordered_by_peak[s]
                                  & ts.spec$noise==noisenames[n],]$spec)
    
    TOT_high[s] <- (totalvar[totalvar$spp==spp_ordered_by_peak[s] 
                             & totalvar$EI==0.72 
                             & totalvar$variable=="Nsize" 
                             & totalvar$noise==noisenames[n],]$variance)*AUC_fraction_high[s]
    
    TOT_low[s] <- (totalvar[totalvar$spp==spp_ordered_by_peak[s]
                            & totalvar$EI==0.72 
                            & totalvar$variable=="Nsize"
                            & totalvar$noise==noisenames[n],]$variance)*AUC_fraction_low[s]
  }
  #store percents for each type of noise
  AUC_amount_highL[[n]] <- AUC_amount_high 
  AUC_amount_lowL[[n]] <-  AUC_amount_low 
  AUC_fraction_highL[[n]] <- AUC_fraction_high 
  AUC_fraction_lowL[[n]] <- AUC_fraction_low
  TOT_highL[[n]] <- TOT_high
  TOT_lowL[[n]] <- TOT_low
  AUC_totalamt_L[[n]] <- AUC_totalamt
  
  print(noisenames[n])
}
rm(n,s)
AUC_amount_highdf <- data.frame(do.call(cbind,AUC_amount_highL))
AUC_amount_lowdf <- data.frame(do.call(cbind,AUC_amount_lowL))
AUC_fraction_highdf <- data.frame(do.call(cbind,AUC_fraction_highL))
AUC_fraction_lowdf <- data.frame(do.call(cbind,AUC_fraction_lowL))
TOT_highdf <- data.frame(do.call(cbind,TOT_highL))
TOT_lowdf <- data.frame(do.call(cbind,TOT_lowL))
AUC_totalamt_df <- data.frame(do.call(cbind,AUC_totalamt_L))

AUC_amount_highdf$spp <- spp_ordered_by_peak
AUC_amount_lowdf$spp <- spp_ordered_by_peak
AUC_fraction_highdf$spp <- spp_ordered_by_peak
AUC_fraction_lowdf$spp <- spp_ordered_by_peak
AUC_totalamt_df$spp <- spp_ordered_by_peak
TOT_highdf$spp <-spp_ordered_by_peak
TOT_lowdf$spp <-spp_ordered_by_peak

# convert dfs to long format
AUC_amount_highdflong <- AUC_amount_highdf %>% 
  gather(noise,value,1:length(noisenames)) %>% 
  mutate(AUCdes=rep("amt_high_spec"))

AUC_amount_lowdflong <- AUC_amount_lowdf %>% 
  gather(noise,value,1:length(noisenames)) %>% 
  mutate(AUCdes=rep("amt_low_spec") )

AUC_fraction_highdflong <- AUC_fraction_highdf %>% 
 gather(noise,value,1:length(noisenames)) %>% 
  mutate(AUCdes=rep("fra_high"))

AUC_fraction_lowdflong <- AUC_fraction_lowdf %>% 
 gather(noise,value,1:length(noisenames)) %>% 
  mutate(AUCdes=rep("fra_low"))

AUC_total_dflong <- AUC_totalamt_df %>% 
  gather(noise,value,1:length(noisenames)) %>% 
  mutate(AUCdes=rep("total_spec"))

TOT_high_dflong <- TOT_highdf %>%
  gather(noise,value,1:length(noisenames)) %>%
  mutate(AUCdes=rep("tot_high_sgm"))

TOT_low_dflong <- TOT_lowdf %>%
  gather(noise,value,1:length(noisenames)) %>%
  mutate(AUCdes=rep("tot_low_sgm"))

AUCdat <- rbind(AUC_amount_highdflong,
                AUC_amount_lowdflong,
                AUC_fraction_highdflong,
                AUC_fraction_lowdflong,
                AUC_total_dflong,
                TOT_high_dflong,
                TOT_low_dflong)
rm(AUC_amount_high,AUC_amount_highdf,AUC_amount_highdflong,AUC_amount_highL,
   AUC_amount_low,AUC_amount_lowdf,AUC_amount_lowdflong,AUC_amount_lowL,
   AUC_fraction_high,AUC_fraction_highdf,AUC_fraction_highdflong,AUC_fraction_highL,
   AUC_fraction_low,AUC_fraction_lowdf,AUC_fraction_lowdflong,AUC_fraction_lowL,
   AUC_totalamt_df,AUC_total_dflong,
   TOT_high,TOT_highdf,TOT_high_dflong,TOT_highL,
   TOT_low,TOT_lowdf,TOT_low_dflong,TOT_lowL)
# add age structure columns to AUCdat
AUCdat$peak <- spawndistmetrics[match(AUCdat$spp,spawndistmetrics$spp),"mode_age"]
AUCdat$maxage <- spawndistmetrics[match(AUCdat$spp,spawndistmetrics$spp),"maxage"]
AUCdat$cvs <- spawndistmetrics[match(AUCdat$spp,spawndistmetrics$spp),"cvs_mode"]

# # # -------------------------------------------------------
# # # Format data to make plots
# # 
# # # a) Is total CV different with ENSO? Higher or lower?
# # #    Plot: amt and fraction low fraction as a function of totalvar
# # df.tot <- totalvar %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>%
# #   filter(EI==0) %>% filter(variable=="Nsize")
# # df.amt <- AUCdat %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>%
# #   filter(AUCdes=="tot_low_sgm") %>% select(spp,noise,value)
# # names(df.amt)[names(df.amt)=="value"]<-"tot_low_sgm"
# # df.fra <- AUCdat %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>%
# #   filter(AUCdes=="fra_low") %>% select(spp,noise,value)
# # names(df.fra)[names(df.fra)=="value"]<-"fra_low"
# # df.splo <- AUCdat %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>%
# #   filter(AUCdes=="amt_low_spec") %>% select(spp,noise,value)
# # names(df.splo)[names(df.splo)=="value"]<-"amt_low_spec"
# # df.totAUC <- AUCdat %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>%
# #   filter(AUCdes=="total_spec") %>% select(spp,noise,value)
# # names(df.totAUC)[names(df.totAUC)=="value"]<-"total_spec"
# # df.combo <- full_join(df.tot,df.amt)
# # df.combo <- full_join(df.combo,df.fra)
# # df.combo <- full_join(df.combo,df.splo)
# # df.combo <- full_join(df.combo,df.totAUC)
# # 
# # 
# # p1 <- ggplot(data=df.combo,aes(x=noise,y=total_spec,shape=spp,color=maxage)) +
# #   geom_point() + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=noise,y=total_spec,group=spp,color=maxage)) +
# #   xlab("Noise") +
# #   ylab("Total AUC\n(in SSB spectrum)") + theme(legend.position="none")
# # 
# # p2 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=noise,y=variance,shape=spp,color=maxage)) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=noise,y=variance,group=spp,color=maxage)) +
# #   ylab("Total variance\n(sigma/CV in SSB time series)") +
# #   xlab("Noise") + theme(legend.position="none")
# # 
# # p3 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=noise,y=fra_low,shape=spp,color=maxage)) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=noise,y=fra_low,group=spp,color=maxage)) +
# #   ylab("Fraction of AUC at low freq\n(in SSB spectrum)") +
# #   xlab("Noise") + theme(legend.position="none")
# # 
# # p4 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=noise,y=tot_low_sgm,shape=spp,color=maxage)) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(aes(x=noise,y=tot_low_sgm,group=spp,color=maxage)) +
# #   ylab("Amount of variance at low freq \n(sigma/mean)*(fraction of AUC at low freq)") +
# #   xlab("Noise") + theme(legend.position="none")
# # 
# # p5 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=noise,y=amt_low_spec,shape=spp,color=maxage)) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(aes(x=noise,y=amt_low_spec,group=spp,color=maxage)) +
# #   ylab("Amount of variance at low freq \n(AUC at low freq in SSB spectrum)") +
# #   xlab("Noise")
# # 
# # 
# # 
# # tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/variance_change_with_noise4.tiff', units="in", width=10, height=6, res=300) 
# # p <- list(p1,p2,p3,p4)
# # do.call(grid.arrange,c(p,ncol=2))
# # dev.off()
# # tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/variance_change_with_noise1.tiff', units="in", width=8, height=5, res=300) 
# #  ggplot(data=df.combo) +
# #   geom_point(aes(x=noise,y=amt_low_spec,shape=spp,color=maxage)) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(aes(x=noise,y=amt_low_spec,group=spp,color=maxage)) +
# #   ylab("Amount of variance at low freq \n(AUC at low freq in SSB spectrum)") +
# #   xlab("Noise")+ theme(legend.direction = "vertical", legend.box = "horizontal")
# # dev.off()
# # 
# # 
# # 
# # # How does the AUC at low freq & fraction
# # # of AUC at low frequencies change when we go
# # # from white to ENSO?
# # p6 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=total_spec,y=fra_low,shape=spp,color=noise),size=2) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=total_spec,y=fra_low,group=spp)) +
# #   ylab("Fraction of AUC at low freq") +
# #   xlab("Total AUC") + theme(legend.position="none")
# # 
# # p7 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=total_spec,y=amt_low_spec,shape=spp,color=noise),size=2) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=total_spec,y=amt_low_spec,group=spp)) +
# #   ylab("Amount of AUC at low freq") +
# #   xlab("Total AUC") + theme(legend.position="none")
# # 
# # p8 <- ggplot(data=df.combo) +
# #   geom_point(aes(x=variance,y=tot_low_sgm,shape=spp,color=noise),size=2) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=variance,y=tot_low_sgm,group=spp)) +
# #   ylab("Amount of variance at low freq \n(sigma/mean)*(fraction of AUC at low freq)") +
# #   xlab("Total variance (sigma/mean)")+ theme(legend.direction = "vertical", legend.box = "horizontal")
# # 
# # tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/lowfreqvar_as_a_function_of_totalvar2.tiff', units="in", width=7, height=4, res=300) 
# # p <- list(p6,p7)
# # do.call(grid.arrange,c(p,ncol=2))
# # dev.off()
# # 
# # tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/lowfreqvar_as_a_function_of_totalvar1.tiff', units="in", width=7, height=5, res=300) 
# # ggplot(data=df.combo) +
# #   geom_point(aes(x=variance,y=tot_low_sgm,shape=spp,color=noise),size=2) + 
# #   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
# #   geom_line(data=df.combo,aes(x=variance,y=tot_low_sgm,group=spp)) +
# #   ylab("Amount of variance at low freq \n(sigma/mean)*(fraction of AUC at low freq)") +
# #   xlab("Total variance (sigma/mean)") + theme(legend.direction = "vertical", legend.box = "horizontal")
# # dev.off()
# # # How does pOFL depend on variability?
# # # Merge freq-dependent var & pOFL data frames (for plots)
# # # match on spp, noise (note: EI=0 for all right now)
# probdf.N <- probdf %>% filter(variable=="Nsize") %>% filter(noise %in% c("white","ENSO","ENSOfast","ENSOslow")) %>% select(spp,noise,probs)
# df.combo.p <- full_join(df.combo,probdf.N)
# head(df.combo.p)
# 
# p9 <- ggplot(data=df.combo.p) +
#   geom_point(aes(x=total_spec,y=probs,shape=spp,color=noise),size=2) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=total_spec,y=probs,group=spp)) +
#   ylab("Fraction of time below OFL") +
#   xlab("Total AUC\n(SSB spectrum)") + theme(legend.position="none")
# 
# p10 <- ggplot(data=df.combo.p) +
#   geom_point(aes(x=variance,y=probs,shape=spp,color=noise),size=2) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=variance,y=probs,group=spp)) +
#   ylab("Fraction of time below OFL") +
#   xlab("Total variance\n(sigma/mean in SSB)") + theme(legend.position="none")
# 
# p11 <- ggplot(data=df.combo.p) +
#   geom_point(aes(x=amt_low_spec,y=probs,shape=spp,color=noise),size=2) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=amt_low_spec,y=probs,group=spp)) +
#   ylab("Fraction of time below OFL") +
#   xlab("Amount of AUC at low freq\n(in SSB spectrum)") + theme(legend.position="none")
# 
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/pOFL_dependence_on_lowfreqvariance.tiff', units="in", width=8, height=6, res=300) 
# ggplot(data=df.combo.p) +
#   geom_point(aes(x=tot_low_sgm,y=probs,shape=spp,color=noise),size=2) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=tot_low_sgm,y=probs,group=spp)) +
#   ylab("Fraction of time below OFL") + 
#   xlab("Amount of variance at low freq \n(sigma/mean)*(fraction of AUC at low freq)") 
#  
# dev.off()
# 
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/pOFL_dependence_on_fractionlowfreq.tiff', units="in", width=8, height=5, res=300) 
# ggplot(data=df.combo.p) +
#   geom_point(aes(x=fra_low,y=probs,shape=spp,color=noise),size=3) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=fra_low,y=probs,group=spp,color=""),color="gray90") +
#   ylab("Fraction of time below OFL") +
#   xlab("Fraction of AUC at low freq\n(in SSB spectrum)") + theme(legend.direction = "vertical", legend.box = "horizontal") + theme_classic() +
#   geom_smooth(aes(x=fra_low,y=probs),color="gray50",method="lm",se=FALSE)
# dev.off()
# 
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/pOFL_dependence_on_variance6.tiff', units="in", width=7, height=8, res=300) 
# p <- list(p9,p10,p11,p12)
# do.call(grid.arrange,c(p,ncol=2))
# dev.off()
# 
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/pOFL_dependence_on_variance1.tiff', units="in", width=6, height=4, res=300) 
# ggplot(data=df.combo.p) +
#   geom_point(aes(x=fra_low,y=probs,shape=spp,color=noise),size=2) + 
#   scale_shape_manual(values=seq(from=0,to=length(unique(totalvar$spp)))) +
#   geom_line(data=df.combo.p,aes(x=fra_low,y=probs,group=spp)) +
#   ylab("Fraction of time below OFL") +
#   xlab("Fraction of AUC at low freq\n(in SSB spectrum)") + theme(legend.direction = "vertical", legend.box = "horizontal")
# dev.off()
# 
# # Plot: difference in pOFL between white and ENSO vs diff in fraction of low frequency variability
# diff.df <- data.frame(cbind(as.character(unique(probdf.N$spp)),
#                  rep(NA,length(unique(probdf.N$spp))),
#                  rep(NA,length(unique(probdf.N$spp))),
#                  rep(NA,length(unique(probdf.N$spp)))),stringsAsFactors = FALSE)
# colnames(diff.df) <- c("spp","noise_pair","lowfreqvar_diff","pofl_diff")
# for(s in 1:length(unique(df.combo.p$spp))){
#   t <- df.combo.p[df.combo.p$spp==unique(df.combo.p$spp)[s],]
#   # subtract low var w/white noise from low var w/ENSO
#   diff.df[diff.df$spp==unique(probdf.N$spp)[s],]$lowfreqvar_diff <- t[t$noise=="white",]$amt_low_spec - t[t$noise=="ENSO",]$amt_low_spec
#   # subtract pofl w/white noise from pofl w/ENSO
#   diff.df[diff.df$spp==unique(probdf.N$spp)[s],]$pofl_diff <- t[t$noise=="white",]$probs - t[t$noise=="ENSO",]$probs
#   # fill in noise-pair
#   diff.df[diff.df$spp==unique(probdf.N$spp)[s],]$noise_pair <- "white-enso" 
# }
# str(diff.df)
# diff.df$lowfreqvar_diff <- as.numeric(diff.df$lowfreqvar_diff)
# diff.df$pofl_diff <- as.numeric(diff.df$pofl_diff)
# diff.df$maxage <- rep(NA,length(diff.df[,1]))
# diff.df$maxage <- spawndistmetrics[match(diff.df$spp,spawndistmetrics$spp),"maxage"]
# 
# p14 <- ggplot(data=diff.df) + 
#   geom_point(aes(x=lowfreqvar_diff,y=pofl_diff,shape=spp,color=maxage),size=2) +
#   geom_hline(yintercept = 0) + geom_vline(xintercept = 0) +
#   xlab("ENSO-white (amount AUC at low freq)") + ylab("ENSO-white (pOFL)") +
#   #geom_smooth(aes(x=lowfreqvar_diff,y=pofl_diff),method='lm',formula=y~x) +
#   ggtitle("Difference in pOFL between\nwhite and ENSO as a function\nof the difference in amount\nof AUC at low freq between\nwhite and ENSO") +
#   scale_shape_manual(name="Species",values=seq(from=0,to=length(unique(df$spp)))) 
# 
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/pOFL_depends_on_noise.tiff', units="in", width=6, height=4, res=300) 
# ggplot(data=df.combo.p) + 
#   geom_point(aes(x=noise,y=probs,shape=spp,color=maxage),size=2) +
#   xlab("ENSO-white (amount AUC at low freq)") + ylab("ENSO-white (pOFL)") +
#   geom_line(aes(x=noise,y=probs,group=spp,color=maxage)) +
#   scale_shape_manual(name="Species",values=seq(from=0,to=length(unique(df$spp)))) 
# dev.off()
# 
# head(ts.spec)
# head(ts.data)
# ggplot(data=ts.spec[ts.spec$spp=="Sardine" &
#                     ts.spec$noise %in% c("white","ENSO") &
#                     ts.spec$variable=="Nsize" &
#                     ts.spec$EI==0.72,]) + 
#   geom_line(aes(x=freq,y=specN,color=noise),size=1) +
#   xlab("Frequency") + ylab("Variance") +
#   theme_bw() + scale_y_log10()
# 
# ggplot(data=ts.data[ts.data$spp=="Sardine" &
#                     ts.data$noise %in% c("white","ENSO") &
#                     ts.data$variable=="Nsize" &
#                     ts.data$EI==0.72,]) + 
#   geom_line(aes(x=year,y=value,color=noise),size=1) +
#   xlab("Frequency") + ylab("Variance") +
#   theme_bw() + scale_y_log10()
# 
# ggplot(data=ts.data[ts.data$spp=="Sardine" &
#         ts.data$FLEP==0.35 &
#         ts.data$variable=="Nsize" &
#         ts.data$noise %in% c("white","ENSO") &
#         ts.data$year %in% rm_first_timesteps:(timesteps-2900),]) +
#   geom_line(aes(x=year,y=value,linetype=noise)) +
#   scale_y_log10() + 
#   geom_hline(data=ts.data[ts.data$spp=="Sardine" &
#         ts.data$FLEP==0.30 &
#         ts.data$variable=="Nsize" &
#         ts.data$noise %in% c("white","ENSO") &
#         ts.data$year %in% rm_first_timesteps:(timesteps-2900),],
#              aes(yintercept = means,linetype=noise)) +
#   scale_color_manual(values=c("black","grey")) +
#   theme_classic() +
#   ggtitle("Sardine") +
#   theme(plot.title = element_text(margin = margin(t = 10, b = -20))) 
# 
#  
#     tempthres <-ts.data[ts.data$spp==spp[s] &
#                           ts.data$FLEP==0.3 &
#                           ts.data$variable=="Nsize" &
#                           ts.data$noise %in% c("white") &
#                           #ts.data$noise==noisenames[n] &
#                           ts.data$year %in% rm_first_timesteps:(timesteps-2900),] 
#     
#     multiplots[[s]] <- ggplot(data=tempts,aes(x=year,y=value,color=noise)) +
#       geom_line() +
#       scale_y_log10() +
#       #scale_y_log10(limits=c(minSSB,maxSSB)) +
#      
#       ggtitle(paste(noisenames[n],"\n",spp[s],"(",spawndistmetrics[spawndistmetrics$spp==spp[s],]$mode_age,")","\nOFL=mean SSB when FLEP=0.3",", FLEP=0.35",sep="")) +
#       ylab("Spawning stock biomass") +
#      #facet_grid(noise ~ variable) +
#      #theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
#      #theme(axis.title.y = element_text(angle = 0)) +
#      theme(legend.position="none",
#            plot.title = element_text(margin = margin(t = 10, b = -20))) +
#       geom_hline(data=tempthres,
#              aes(yintercept = means)) 
#     
# # Plot: show fraction of low freq variance vs max age and peak age
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/fig1g_fralow_vs_maxage.tiff', units="in", width=6, height=4, res=300) 
# ggplot(data=df.combo[df.combo$EI==0 & 
#                      df.combo$variable=="Nsize" &
#                      df.combo$noise=="white",],aes(x=maxage,y=fra_low)) +
#   geom_point() + xlab("Maximum Age (yrs)") + ylab("Fraction of total variance\nin low frequencies") +
#   geom_label_repel(aes(label=spp),label.size=NA,) +
#   theme_classic()
# dev.off()
#   
# # Plot barplot: for each species (maybe only 5?) bar for pOFL in each noise
# tiff(file='C:/Users/Mikaela/Documents/GitHub/pfmc/results/fig5_barplot.tiff', units="in", width=8, height=4, res=300) 
# noise_levels <- c("white","ENSO","ENSOfast","ENSOslow")
# df.combo.p$noise <- factor(df.combo.p$noise,levels=noise_levels)
# spawndistmetrics$spp_max <- paste(spawndistmetrics$spp," (",spawndistmetrics$maxage,")",sep="")
# spp_levels_maxage <- spawndistmetrics[order(spawndistmetrics$maxage),]$spp_max 
# df.combo.p$spp_max <- paste(df.combo.p$spp," (",df.combo.p$maxage,")",sep="")
# df.combo.p$spp_max <- factor(df.combo.p$spp_max, levels=spp_levels_maxage)
# ggplot(data=df.combo.p[df.combo.p$variable=="Nsize",],
#        aes(x=spp_max,y=probs, fill=noise)) +
#   geom_bar(stat = "identity",position = position_dodge()) +
#   theme_bw() + theme(axis.text.x = element_text(angle = 50, hjust = 1)) +
#   scale_fill_grey() + ylab("Fraction of time below OFL") + xlab("")
# dev.off()